GO

### 2019-12-12 analysis/12_GO.Rmd
better markdown
more readable comment

```{r}
library(tidyverse)
library(knitr)
library(kableExtra)

@@

## The code

@@

kable(one) 
# top GOs of these genes: endocrine porcess, regulation of blood pressure (by hormones or chemical signals), system process, regulation of hormone levels

kable(two) 
# top Gos maternal, parental, reproductive behavior; reproduction, reproductive process

kable(three) 
# response to chemical, maternal and parental beahviors, regulation of RNApolI transscription

kable(four) 
# insuffiencient genes

kable(five) 
# (cellular) response to organic substance, endocrine process, response to stimulus, response to chemical

kable(six)  
# insuffiencient genes

kable(seven)  
# endocrine process, system process, hormone transport, synaptic transmission (dopamineric), secretion by cell

kable(eight) 
# (positive) regulation of gap junction assembly, regulation of cardiac conduction, regualation of blood pressure
```

>>>>

## Made with these R packages

```{r setup}
library(tidyverse)
library(knitr)
library(kableExtra)

@@

@@

# top GOs of these genes: endocrine porcess, 
#regulation of blood pressure (by hormones or chemical signals), 
#system process, regulation of hormone levels
kable(one)

# top Gos maternal, parental, reproductive behavior; 
# reproduction, reproductive process
kable(two)

# response to chemical, maternal and parental behaviors, 
# regulation of RNApolI transcription
kable(three)

# insuffiencient genes for GO analysis
kable(four)

# (cellular) response to organic substance, endocrine process, 
# response to stimulus, response to chemical 
kable(five)

# insuffiencient genes
kable(six)

# endocrine process, system process, hormone transport, 
# synaptic transmission (dopamineric), secretion by cell
kable(seven)

# (positive) regulation of gap junction assembly, 
# regulation of cardiac conduction, regualation of blood pressure
kable(eight) 
```
